Regional-scale Base-flow Index of Gauged and Ungauged Basins in Drylands

### 2024-11-26 index.qmd
sdf
Update index.qmd

Statisical analyses were performed on mean annual BFI values of instrumented streamgages. We examined the presence of temporal trends in mean annual BFI using the Mann-Kendall nonparametric trend test [@kendall1970; @mann1945nonparametric]. The Mann-Kendall was used to determine trends in BFI and trend significance of gauged reaches during their period of record.

@@

@@

: Table 2. Performance of model predictions for BFI for all sites split by various classifications. n is number of sites, R^2^ is the coefficient of determination of a linear regression, MSE is mean-squared-error, RMSE is root-mean-squared-error, MAE is mean-absolute-error, NSE is Nash-Sucliffe efficiency, and pbias is percent bias. {#tbl-performance}

>>>>

Statisical analyses were performed on mean annual BFI values of instrumented streamgages. We examined the presence of temporal trends in mean annual BFI using the Mann-Kendall nonparametric trend test [@kendall1970; @mann1945nonparametric]. The Mann-Kendall test was used to determine trends in BFI and trend significance of gauged reaches.

@@

| Classification Group         |   n | n_pos | n_neg | perc_pos | perc_neg |
|:-----------------------------|----:|------:|------:|---------:|---------:|
| Climate - Monsoon Dominated  |  94 |    10 |    23 |    0.106 |    0.245 |
| Climate - Snowmelt Dominated | 150 |    19 |    17 |    0.127 |    0.113 |
| PhysRegion - Basin&Range     | 190 |    26 |    33 |    0.137 |    0.174 |
| PhysRegion - CO Plateau      |  54 |     3 |     7 |    0.056 |    0.130 |
| Climate - Warm-Wet           |  31 |     3 |     6 |    0.097 |    0.194 |
| Climate - Warm-Dry           |  81 |    15 |    16 |    0.185 |    0.198 |
| Climate - Cool-Wet           |  83 |     6 |    11 |    0.072 |    0.133 |
| Climate - Cool-Dry           |  49 |     5 |     7 |    0.102 |    0.143 |
| Slope - High                 | 111 |    12 |    15 |    0.108 |    0.135 |
| Slope - Low                  | 133 |    17 |    25 |    0.128 |    0.188 |

: Table 2. Comparison of trends for BFI for all sites split by various classifications. Only sites with a significant ($\rho \le 0.05$) trend are included here as established by a Mann-Kendall test for monotonic trends across the full period of record. n is the number of sites, n_pos (n_neg) is the number of sites with positive (negative) trends, perc_pos (perc_neg) is the percentage of n with a positive (negative) trend. {#tbl-trends}

@@

: Table 3. Performance of model predictions for BFI for all sites split by various classifications. n is number of observatios, R^2^ is the coefficient of determination of a linear regression, MSE is mean-squared-error, RMSE is root-mean-squared-error, MAE is mean-absolute-error, NSE is Nash-Sucliffe efficiency, and pbias is percent bias. {#tbl-performance}
